Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.Rmd
Updates to keywords and abstract

abstract: |
  Social mobilization requires effective collective coordination. In recent years, individuals involved in social movements have taken to social media platforms such as Twitter to reach broader audiences at rapid speeds. Effective virtual mobilization similarly requires social cohesion and coordination, yet it is still unclear if virtual mobilization reflects real-world movements. Here, we explore the dynamics of real-world events and social cohesion on Twitter in Syria during the Arab Spring. Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigate if counts of all daily events, daily positive events, and daily negative events are coupled with social cohesion found in Syrian tweets. Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day, but not with counts of positive events. This suggests that virtual mobilization does reflect real-world movements, but only for salient, frequent and negative events. We conclude with a discussion of implications and applications of nonlinear methods in political science research.
  <!-- https://tinyurl.com/ybremelq -->

keywords          : "Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring"
wordcount         : "X"

>>>>

abstract: |
  Social mobilization requires effective collective coordination. In recent years, individuals involved in social movements have taken to social media platforms to reach broader audiences at rapid speeds. Effective virtual mobilization similarly requires social cohesion and coordination, yet the degree to which virtual mobilization reflects or drives real-world movements is unclear. Here, we explore the dynamics of real-world events and social cohesion on Twitter in Syria during the Arab Spring. Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigate if counts of all daily events, daily positive events, and daily negative events are coupled with social cohesion found in Syrian tweets. Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day but not with counts of positive events. This suggests that virtual mobilization does reflect real-world movements but only for salient, frequent, and negative events. We conclude with a discussion of implications and applications of nonlinear methods in political science research.
  <!-- https://tinyurl.com/ybremelq -->

keywords          : "social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring"
wordcount         : "X"
